\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2020-08-25 sections/abstract.tex
Updates from Overleaf

\begin{abstract}
  {
    \noindent
    Microbes tend to organize into communities consisting of hundreds of species involved in complex interactions with each other.
    16S ribosomal RNA (16S rRNA) amplicon profiling provides snapshots that reveal the phylogenies and abundance profiles of these microbial communities.
    These snapshots, when collected from multiple samples, have the potential to reveal which microbes co-occur, providing a glimpse into the network of influences in these communities.
    The inference of networks from 16S data is prone to statistical artifacts.
    There are many tools for performing each step of the 16S analysis workflow, but the extent to which these steps affect the final network is still unclear.
    In this study, we perform a meticulous analysis of each step of a pipeline that processes 16S sequencing data into a network of microbial associations.
    Through this process, we map how different choices of algorithms and parameters affect the co-occurrence network, and estimate steps which contribute most significantly to the variance. We further determine the tools and parameters that generate the most accurate and robust co-occurrence networks, based on comparison with mock and synthetic datasets.
    Ultimately, we develop a standardized pipeline that follows these default tools and parameters, but that can also help explore the outcome of any other combination of choices.
    We envisage that this pipeline for processing 16S sequencing data into networks of microbial co-occurrences could be used for integrating multiple data-sets, and for generating comparative analyses and consensus networks useful for detecting disease-related patterns.
        The pipeline is available as a Python package at \href{https://github.com/segrelab/MiCoNE}{https://github.com/segrelab/MiCoNE}
  }
\end{abstract}

>>>>

\begin{abstract}
  {
    \noindent
    Microbes tend to organize into communities consisting of hundreds of species involved in complex interactions with each other.
    16S ribosomal RNA (16S rRNA) amplicon profiling provides snapshots that reveal the phylogenies and abundance profiles of these microbial communities.
    These snapshots, when collected from multiple samples, have the potential to reveal which microbes co-occur, providing a glimpse into the network of influences in these communities.
    The inference of networks from 16S data is prone to statistical artifacts.
    There are many tools for performing each step of the 16S analysis workflow, but the extent to which these steps affect the final network is still unclear.
    In this study, we perform a meticulous analysis of each step of a pipeline that processes 16S sequencing data into a network of microbial associations.
    Through this process, we map how different choices of algorithms and parameters affect the co-occurrence network, and estimate steps which contribute most significantly to the variance. We further determine the tools and parameters that generate the most accurate and robust co-occurrence networks, based on comparison with mock and synthetic datasets.
    Ultimately, we develop a standardized pipeline that follows these default tools and parameters, but that can also help explore the outcome of any other combination of choices.
    We envisage that this pipeline for processing 16S sequencing data into networks of microbial co-occurrences could be used for integrating multiple data-sets, and for generating comparative analyses and consensus networks that can help understand and control microbial community assembly in different biomes. 
        The pipeline is available as a Python package at \href{https://github.com/segrelab/MiCoNE}{https://github.com/segrelab/MiCoNE}
  }
\end{abstract}

### 2020-08-25 sections/acknowledgments.tex
Updates from Overleaf

\section*{Acknowledgments}

  We are grateful for ...

>>>>

% TODO: Update this section
\section*{Acknowledgments}

We are grateful to members of the Segrè lab for helpful discussions and for feedback on the manuscript. This work was partially funded by grants from the National Institutes of Health (National Institute of General Medical Sciences, award R01GM121950; National Institute of Dental and Craniofacial Research, award number R01DE024468; and National Institute on Aging, award number UH2AG064704), the U.S. Department of Energy, Office of Science, Office of Biological & Environmental Research through the Microbial Community Analysis and Functional Evaluation in Soils SFA Program (m-CAFEs) under contract number DE-AC02-05CH11231 to Lawrence Berkeley National Laboratory, the National Science Foundation (grant NSFOCE-BSF 1635070), the Human Frontiers Science Program (RGP0020/2016), and the Boston University Interdisciplinary Biomedical Research Office.

\section*{Contributions}
Designed the research project: DK, KK, DS, ZH, CDL. Performed analysis: DK, GB. Wrote the first draft of the manuscript: DK. Revised and wrote final version of the manuscript: DK, DS, KK.
